Tensor anisotropy as a tracer of cosmic voids

### 2015-03-18 cosmic_voids.tex
revised abstract and conclusions

\begin{abstract}
We present a new method to find voids in cosmological simulations
based on the tidal and the velocity shear tensors
definitions of the cosmic web. 
We use the fractional anisotropy (FA) computed from the eigenvalues
of each web scheme as a void tracer.
We identify voids using a watershed transform based on the local
minima of the FA field without making any assumption on the shape or
structure of the voids.  
We test the method on the Bolshoi simulation and report on the
abundance and radial averaged profiles for the density, velocity and
fractional anistropy.
We find that voids in the velocity shear web are smaller than voids in
the tidal web, with a particular overabundance of very small voids in
the inner region of filaments/sheets.
We clasify voids as subcompensated/overcompansated depending on the
absence/presence of an overdense matter ridge in their density
profile, finding that close to $65\%$ and $35\%$ of the total
population are classified into each category, respectively.
Finally, we find evidence for the existence of universal profiles once the
radial coordinate is normalized to the effective radius of each void
from the radiallly averaged profiles for density, velocity and
fractional anisotropy. 
Put together, all these results show that the FA is a reliable tracer
for voids, which can be used in complementarity to other existing
methods and tracers.
\end{abstract}

@@

In this paper we propose that the anisotropy of the eigenvalues from
tidal and velocity shear tensors is a good tracer of  cosmic voids. 
Based on this idea we go on to implement a watershed
algorithm o the fractional anisotropy to find voids in a N-body
cosmological simulation.
We perform different test on the voids found on the anisotropy of two
tensorial schemes, the T-Web and the V-web.

The first quantity examine is the void size distribution
characterized by an effective radius. 
We find that for T-Web voids the shape of this function corresponds to
standard expectations from a two-barrier setup. 
However, for the V-Web we find an overabundance of the smallest voids.
This is due to artifacts in the web finding scheme in sheets and also
to the smaller fragmented voids inside the largest voids already
identified in the T-Web. 
The void fragmentation hints at a complex velocity structure in large
voids compared to its simpler density/gravitational potential anatomy.

A second step in the characterization of the voids found by our method
is the separation into subcompensated and overcompensated samples. 
In the T-Web $35\%$ of the voids are overcompensated ($65\%$
subcompensated), meaning that they are located in denser regions with
a clear delimiting ridge.   
For the V-web the subcompensated fraction rises from $65\%$ to $85\%$ as the
void size decreases, supporting the picture of smaller spurious voids
located in low density matter sheets.

@@

The Fractional Anisotropy profiles also show remarkable similarities,
(inside each class of subcompensated and overcompensated voids)
and a close correlation with the behaviour in the density and velocity
profiles. 
From these profiles it becomes clear that the limit of overcompensated
void coincides with a ridge in of FA values close to $0.9$. 
This value is close to the limit FA=$0.95$ we impose in the watershed
algorithm, indicating that these voids are very close to spherical.
For the subcompensated voids the FA quickly increases to FA values of 
$\sim 0.7-0.8$ at $r/r_{\rm eff}\sim 1$ to find a plateau, which is
quite far from the limiting FA$=0.95$ suggesting that these voids are
far from spherical.

Put together, the results for the radially averaged profiles support the 
evidence for a universal density profile.  
This extends the work done
by \cite{Hamaus14} to smaller void sizes.

@@

We would like to thank Nelson Padilla for helpful comments and suggestions
on the manuscript.

>>>>

\begin{abstract}
We present a new method to find voids in cosmological simulations
based on the tidal and the velocity shear tensors
definitions of the cosmic web. 
We use the fractional anisotropy (FA) computed from the eigenvalues
of each web scheme as a void tracer.
We identify voids using a watershed transform based on the local
minima of the FA field without making any assumption on the shape or
structure of the voids.  
We test the method on the Bolshoi simulation and report on the
abundance and radial averaged profiles for the density, velocity and
fractional anistropy.
We find that voids in the velocity shear web are smaller than voids in
the tidal web, with a particular overabundance of very small voids in
the inner region of filaments/sheets.
We clasify voids as subcompensated/overcompansated depending on the
absence/presence of an overdense matter ridge in their density
profile, finding that close to $65\%$ and $35\%$ of the total
population are classified into each category, respectively.
Finally, we find evidence for the existence of universal profiles from
the radially averaged profiles for density, velocity and fractional
anisotropy. 
This requires that the radial coordinate is normalized to the
effective radius of each void. 
Put together, all these results show that the FA is a reliable tracer
for voids, which can be used in complementarity to other existing
methods and tracers.
\end{abstract}

@@

In this paper we propose that the anisotropy of the eigenvalues from
tidal and velocity shear tensors is a good tracer of  cosmic voids. 
Based on this idea we go on to implement a watershed
algorithm on the fractional anisotropy to find voids in a N-body
cosmological simulation.
We perform different test on the voids found on the anisotropy of two
tensorial schemes, the T-Web and the V-web.

The first quantity we examine is the void size distribution
characterized by an effective radius. 
We find that for the T-Web scheme the void size distribution has a
shape consistent with standard expectations from a two-barrier setup. 
However, for the V-Web we find an overabundance of the smallest voids.
This is due to two reasons. 
First, there are artifacts in the web
finding scheme inside sheets. 
Second, there V-web produces smaller
fragmented voids inside the largest voids found in the T-Web
classification.  
This void fragmentation hints at a complex velocity structure in large
voids compared to its simpler density/gravitational potential anatomy.

A second step in the void characterization 
is the separation into subcompensated and overcompensated samples. 
In the T-Web $35\%$ of the voids are overcompensated ($65\%$
subcompensated), meaning that they are located in denser regions with
a clear delimiting ridge.   
For the V-web the subcompensated fraction rises from $65\%$ to $85\%$ as the
void size decreases, supporting the picture of smaller spurious voids
located in medium density matter sheets.

@@

The Fractional Anisotropy profiles also show remarkable similarities
inside each class of subcompensated and overcompensated voids
and a close correlation with the behaviour in the density and velocity
profiles. 
From these profiles it becomes clear that the limit of overcompensated
void coincides with a ridge in of FA values close to $0.9$. 
This value is close to the limit FA=$0.95$ we impose in the watershed
algorithm, indicating that these voids are very close to spherical.
For the subcompensated voids the FA quickly increases to FA values of 
$\sim 0.7-0.8$ at $r/r_{\rm eff}\sim 1$ to find a plateau, which is
quite far from the limiting FA$=0.95$ suggesting that these voids are
far from spherical.

Put together, the results for the radially averaged profiles support the 
evidence for a universal density profile.  
Our results extends to smaller void sizes the work done by
\cite{Hamaus14} on simulations and by \cite{Ceccarelli13} on SDSS data.

@@

We would like to thank Rien van de Weygaert for his thoughtful review
and  very helpful suggestions on this manuscript.  
We also thank Nelson Padilla and Yehuda  Hoffman for their comments on
the manuscript.  
SB also thanks Juan Carlos Mu\~noz-Cuartas 
for many clarifying discussions and helpful ideas.
JEFR acknowledges financial support from Vicerrector\'ia de
Investigaciones at Universidad de los Andes (Colombia) through a FAPA
grant.
